Mixed language processing increases cross-language phonetic transfer in Bengali-English Bilinguals

### 2021-05-24 draft_glossa-psych/glossa-psych_AM-ID_manuscript.tex
emdashes added

Paradigm did affect vowel quality, but this applied uniformly across experimental conditions-- all vowels were more backed and lowered in the code-switching task. Given that at least for F1, the effect is limited to the early stages of articulating the vowel, it is plausible that this lowering is an artifact of the particular stimuli used here-- resulting from some corarticulatory effect that was absent in the picture-naming task. While this is intriguing, it is beyond the scope of the present study.

>>>>

Paradigm did affect vowel quality, but this applied uniformly across experimental conditions---all vowels were more backed and lowered in the code-switching task. Given that at least for F1, the effect is limited to the early stages of articulating the vowel, it is plausible that this lowering is an artifact of the particular stimuli used here---resulting from some corarticulatory effect that was absent in the picture-naming task. While this is intriguing, it is beyond the scope of the present study.
